\vspace{-2.25cm} Multimodal Abnormity-Aware Model\\for Ocular Disease Diagnosis

### 2024-08-31 Paper/Paper.tex
write conclusion

	TEXT: abstract

@@

	TEXT: conclusion

>>>>

	We develop a novel model called the Multimodal Abnormity-Aware Model, which uses optical coherence tomography (OCT) and color fundus images to diagnose ocular diseases. The model is composed of the Abnormity Models, which use OCT images to identify 11 abnormities and fundus images to identify 8 abnormities, and the Diagnosis Model, which diagnoses 12 diseases by integrating information from the Abnormity Models. We use an abnormity-to-disease approach and simulate the decision-making process of ophthalmologists. Information integration is achieved through employing a fusion mechanism.  We also introduced codominant abnormities and diseases, providing more information for reference.

@@

	We developed the Multimodal Abnormity-Aware Model, which takes both OCT and fundus images as input. We integrate information from different sources by employing the fusion mechanism. Moreover, we use an abnormity-to-disease approach and simulate the decision-making process of ophthalmologists. We also introduced codominant abnormities and diseases, providing more information for reference.

	The main goal of this study is to devise a novel model and verify its feasibility. The MAAM still has room for improvement, such as gathering more authentic data, introducing the expertise of ophthalmologists, refining the Abnormity-to-Disease Deduction Criteria, and improving the structure of the Diagnosis Model.
